---
title: "HW9_SDS315"
author: "Anh Doan (atd2354)"
output:   
  html_document:
    toc: true
    toc_float: true
    toc_collapsed: true
    toc_depth: 3
    theme: lumen
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r}
library(tidyverse)
library(ggplot2)
library(kableExtra)
library(mosaic)
library(broom)

solder <- read_csv("solder.csv")
groceries <- read_csv("groceries.csv")
```

[My GitHub Repository](https://github.com/anhdoan0611/HW9_SDS315)


# **Problem 1: Manufacturing Flaws in Circuit Boards**

### **Part A: Plots**

##### **Opening Size vs Number of Skips**

```{r}
ggplot(solder) +
  geom_boxplot(aes(x = Opening, y = skips, fill = Opening)) +
  labs(
    title = "Number of Solder Skips by Gun Opening Size",
    x = "Solder Gun Opening Size",
    y = "Number of Skips"
  ) +
  theme_minimal()
```

- The plot shows that as the gun opening size decreases, the number of skips also decreases

##### **Alloy Thickness vs Number of Skips**

```{r}
ggplot(solder) +
  geom_boxplot(aes(x = Solder, y = skips, fill = Solder)) +
  labs(
    title = "Number of Solder Skips by Alloy Thickness",
    x = "Alloy Thickness",
    y = "Number of Skips"
  ) +
  theme_minimal()
```

- Based on the plot, thin openings tend to produce a higher number of skips than thick openings.

### **Part B: Regression Model**

```{r}
lm1 <- lm(skips ~ Opening * Solder, data = solder)

cfi <- tidy(lm1, conf.int = TRUE)
print(cfi[, c("term", "estimate", "conf.low", "conf.high")])
```

### **Part C: Interpretation**

- For a large opening with thick solder, the model predicts 0.393 skips. A medium opening adds 2.407 skips, a small opening adds 5.127, and thin solder adds 2.280. The medium & thin interaction subtracts 0.740 skips, while the small & thin interaction adds 9.653 skips beyond those main effects.

### **Part D: Recommendation**

- Based on the model, using a large opening with thick solder is ideal, since it yields the fewest skips in the manufacturing process.

# **Problem 2: Grocery Store Prices**

### **Part A: Price Differences vs Stores**

```{r}
avg_price <- aggregate(Price ~ Store, data = groceries, FUN = mean)

ggplot(avg_price) +
  geom_bar(aes(x= reorder(Store, Price), y = Price), stat = "identity", fill = "#43a2ca") +
  coord_flip() +
  labs(
    title = "Average Product Price by Stores",
    x = "Store",
    y = "Price ($)"
  ) +
  theme_minimal()
```

### **Part B: Availability of Products Across Stores**

```{r}
store_counts <- aggregate(Store ~ Product,
                          data = groceries,
                          FUN  = function(x) length(x))

ggplot(store_counts) +
  geom_bar(aes(x= reorder(Product, Store), y = Store), stat = "identity", fill = "salmon", width = 0.8) +
  coord_flip() +
  labs(
    title = "Availability of Products Across Stores",
    y = "Number of Stores",
    x = "Store"
  ) +
  theme_minimal() +
  theme(
    axis.text.y = element_text(size = 7),
    plot.title = element_text(face = "bold"),
  )
```

### **Part C: Model for Price versus Product and the Type of Store**

```{r}
type_lm <- lm(Price ~ Product + Type, data = groceries)
ci <- confint(type_lm, level = 0.95)
tail(ci,3)
```

### **Part D: Regression Model for Price vs. Product & Store**

##### **Central Market vs H-E-B**

```{r}
store_lm <- lm(Price ~ Product + Store, data = groceries)
tidy_store <- tidy(store_lm)

store_terms <- tidy_store %>%
  filter(str_detect(term, "^Store"))
```

##### **Two Cheapest Stores**

```{r}
# 3. Two cheapest
store_terms %>%
  arrange(estimate) %>%
  slice(1:2)
```

##### **Two Priciest Stores**

```{r}
store_terms %>%
  arrange(desc(estimate)) %>%
  slice(1:2)
```

### **Part E: Price Discrimination**

```{r}
groceries$Store <- relevel(factor(groceries$Store), ref = "H-E-B")

# refit the model
store_lm1 <- lm(Price ~ Product + Store, data = groceries)
tidy_store <- tidy(store_lm1)

coef(store_lm)["StoreCentral Market"]

store_terms <- tidy_store[grep("^Store", tidy_store$term), ]
```

##### **Cheapest store effect compared to H-E-B**

```{r}
store_terms <- store_terms[order(store_terms$estimate), ]

cheapest_store <- store_terms[1, ]

print(cheapest_store)
```

##### **Priciest store effect compared to H-E-B**

```{r}
store_terms <- store_terms[order(store_terms$estimate), ]

priciest_store <- tail(store_terms,1)

print(priciest_store)
```

##### **Interpretation**

- The regression model shows that Central Market’s prices are about **7.3 cents** higher per item than H‑E‑B’s. In turn, H‑E‑B prices are approximately **3.5 cents** above Walmart (the cheapest store) and **1.01 dollars** below Whole Foods (the priciest), for a total **1.36 dollars** gap between the cheapest and priciest stores.

### **Part F: Income**

```{r}
groceries$Income10K <- groceries$Income / 10000

lm_income <- lm(Price ~ Product + Income10K, data = groceries)
tidy_income <- tidy(lm_income)

income_effect <- tidy_income[tidy_income$term == "Income10K", ]
income_effect
```

- The regression model shows that higher average incomes are linked to lower prices, implying that poorer ZIP codes end up paying more for the same items.
- A one-standard deviation increase in the income of a ZIP code seems to be associated with
a **–0.014** standard-deviation change in the price that consumers in that ZIP code expect to pay for
the same product.

# **Problem 3: Redlining**

- **Statement A**: TRUE - There is a clear upward trend of correlation in figure A1. Additionally, based on the regression model, the coefficient is 0.014, suggesting that an increase in the percentage of minority residents is associated with about 0.014 more FAIR policies per 100 units. The R-squared value is approximately 0.52, which shows that there is a moderate positive correlation between the two variables.
 
- **Statement B**: UNDECIDABLE - There is no regression model for the interaction between minority percentage and the housing stock age. The only reported regression treats minority percentage and housing age as separate predictors.

- **Statement C**: TRUE/AMBIGOUS - With an interaction coefficient of –0.01 for minority:fire_riskLow, low‑fire‑risk ZIP codes exhibit a weaker association, though the effect is not significant.

- **Statement D**: FALSE - In model D1 (no income), the minority coefficient is 0.014. However, when income is added in D2, it falls to 0.010—showing that income does not eliminate the minority effect.

- **Statement E**: TRUE - Based on model E, The minority coefficient is +0.008 with a p‑value of 0.006, making it a statistically significant predictor. 